---
title: "movie rating"
author: "GAN LING"
date: "2017/4/12"
output: 
  html_document: 
    fig_width: 15
---

#### load data

```{r}
library(ggplot2)
# before doing this, you need to use python to run the edit_users_movies_dat.py
# file to clean the dat data
# deal with users_clean.dat
users = read.csv("users_clean.dat", sep = "=", header = FALSE, col.names = c("UserID","Gender","Age","Occupation","Zip-code"))
# deal with movies_utf8_clean.dat
movie = read.csv("movies_utf8_clean.dat", sep = "=", header = FALSE, col.names = c("MovieID","Title","Genres"))
# deal with training_ratings_for_kaggle_comp.csv
# training_ratings = read.csv("training_ratings_for_kaggle_comp.csv")
# save(training_ratings, file = "training_ratings.RData")
load("training_ratings.RData")
```

#### combine the data, because this needs time, we can save the result for next time, this part we use one and half an hour to deal with the data and get 116858 observasions.

```{r}
# combine_user = function (users, training_ratings, stopnum){
#     k = 1
#     for (d in training_ratings$user){
#         if (d > stopnum){
#             break
#         }
#         temp_row = data.frame(users[users$UserID == d, c(2,3,4)])
#         print(temp_row)
#         if (k == 1){
#             temp_get = temp_row
#             k = 0
#         }
#         else{
#             temp_get = rbind(temp_get, temp_row)
#         }
#     }
#     cbind(training_ratings[1:nrow(temp_get),], temp_get)
# }
# # get all of the data out when the rating equal to 5. Because we only care about the data with the highest evaluation.
# newraitings = combine_user(users, training_ratings[training_ratings$rating==5,], 6040)
# save(newraitings, file = "newraitings1.RData")

#load the data we save to save time
load("newraitings1.RData")
```

clean the data

```{r}
# see the structure of the data
str(newraitings)
# the column occupation is the index for the job of the evaluation person, then this column should be factor
newraitings$Occupation = as.factor(newraitings$Occupation)
# movie and user columns are also factors
newraitings$user = as.factor(newraitings$user)
newraitings$movie = as.factor(newraitings$movie)
# then we don't need rating and id columns anymore
newraitings = subset(newraitings, select = c(1, 2, 5, 6, 7))
str(newraitings)
head(newraitings, 10)
```

1. the simplest way is to calculate the amount of the 5 star movies and sort them in decresing order, then we can get the best movies for us

```{r}
bestmovie1 = as.matrix(head(sort(table(newraitings$movie), decreasing = TRUE),10))
bestmovie1 = as.data.frame(bestmovie1)
names(bestmovie1) = "count"
bestmovie1 = cbind("movie_id" = rownames(bestmovie1), bestmovie1)
rownames(bestmovie1) <- NULL
```

find the movie information for the table

```{r}
# let the movie_id to factor first
movie$MovieID = as.factor(movie$MovieID)
k = 1
for (i in bestmovie1$movie_id){
    temp_row = data.frame(movie[movie$MovieID == i, c(2, 3)])
    if (k == 1){
        temp_get = temp_row
        k = 0
    }
    else{
        temp_get = rbind(temp_get, temp_row)
    }
}
bestmovie1 = cbind(bestmovie1[1:nrow(temp_get),], temp_get)
```

*For this approach, out ten highest movies are:*

```{r}
bestmovie1$Title
# define the function to draw the 5 best movies
draw_best_movie = function (dataset, figuretitle = "Best Movie and the Support Number"){
    ggplot(data=dataset[1:5,], aes(x=reorder(Title, count[5:1]), fill=reorder(Title, count[5:1]), y = count)) +
    geom_bar(stat="identity" , width = 0.6) +
    geom_text(label=dataset[1:5,]$count, colour = "red", vjust=-0.2) +
    ggtitle(figuretitle) +
    labs(y="Support Number for this Movie", x="Movie", fill = "Movie Title") +
    theme_bw()
    
}
draw_best_movie(bestmovie1)
```

2. select the best movie group by Age

How many observers do we have? assemble the user information

```{r}
user_freq = as.data.frame(table(newraitings$user))
colnames(user_freq) = c("user_id", "5_star_count")
# write the user information in it
users$UserID = as.factor(users$UserID)
k = 1
for (d in user_freq$user_id){
    temp_row = data.frame(users[users$UserID == d, c(2,3,4)])
    if (k == 1){
        temp_get = temp_row
        k = 0
    }
    else{
        temp_get = rbind(temp_get, temp_row)
    }
}
user_freq = cbind(user_freq[1:nrow(temp_get),], temp_get)
```

*draw some pictures*

===================================

see the relation for the gender of the users

```{r}
Agefill = as.factor(user_freq$Age)
ggplot(data=user_freq, aes(x=Gender, fill=Agefill)) +
    geom_bar() +
    ggtitle("Gender") +
    labs(y="Number of Gender", x="Gender", fill = "Age") +
    theme_bw()
```

From the picture we can see that there are two times of male than female in our sample

Then draw the barplot for the age (because there are only seven different age)

```{r}
table(user_freq$Age)
ggplot(data=user_freq, aes(x=Age, fill=Agefill)) +
    geom_bar() +
    ggtitle("Age") +
    labs(y="Number of this Age", x="Age", fill = "Age") +
    theme_bw()
```

now from the result we can see that some observers have the age equal to 1, then they are not valid data, we need to clean them

```{r}
newraitings = newraitings[newraitings$Age != 1, ]
user_freq = user_freq[user_freq$Age != 1, ]
table(user_freq$Age)
```

Then the age can divide into six group, 18   25   35   45   50   56 

```{r}
library(psych)
# define the function first
get_best_movies = function(age, number = 10){
    bestmovie = as.matrix(head(sort(table(newraitings[newraitings$Age==age,]$movie), decreasing = TRUE),number))
    bestmovie = as.data.frame(bestmovie)
    names(bestmovie) = "count"
    bestmovie = cbind("movie_id" = rownames(bestmovie), bestmovie)
    rownames(bestmovie) <- NULL
    
    k = 1
    for (i in bestmovie$movie_id){
    temp_row = data.frame(movie[movie$MovieID == i, c(2, 3)])
    if (k == 1){
        temp_get = temp_row
        k = 0
    }
    else{
        temp_get = rbind(temp_get, temp_row)
    }
}
    bestmovie = cbind(bestmovie[1:nrow(temp_get),], temp_get)
    return(bestmovie)
    
}

# Then run the function to get the result:
# for the group age 18
bestmovie2 = get_best_movies(18)
bestmovie2$Title
draw_best_movie(bestmovie2, figuretitle = "Best Movie and the Support Number for Age 18")
# for the group age 25
bestmovie2 = get_best_movies(25)
bestmovie2$Title
draw_best_movie(bestmovie2, figuretitle = "Best Movie and the Support Number for Age 25")
# for the group age 35
bestmovie2 = get_best_movies(35)
bestmovie2$Title
draw_best_movie(bestmovie2, figuretitle = "Best Movie and the Support Number for Age 35")
# for the group age 45
bestmovie2 = get_best_movies(45)
bestmovie2$Title
draw_best_movie(bestmovie2, figuretitle = "Best Movie and the Support Number for Age 45")
# for the group age 50
bestmovie2 = get_best_movies(50)
bestmovie2$Title
draw_best_movie(bestmovie2, figuretitle = "Best Movie and the Support Number for Age 50")
# for the group age 56
bestmovie2 = get_best_movies(56)
bestmovie2$Title
draw_best_movie(bestmovie2, figuretitle = "Best Movie and the Support Number for Age 56")
```

